The \emph{FrobeniusThresholds} package for \emph{Macaulay2}

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
Edits to Section 2 of paper

We conclude this subsection by briefly reviewing some natural generalizations.  Suppose that $I$ and $J$ are ideals.  If $I$ is contained in the radical of $J$, then we set
%
\[ \nu_I^J(p^e) = \max \{ n : I^n \notin J^{[p^e]} \}. \]  
Otherwise, we set $\nu_I^J(p^e) = \infty$.  
This clearly generalizes the quantity $\nu_f^{\idealm}(p^e)$ considered earlier, and we call 
\[ \ft^J(I) := \lim_{e \to \infty} \frac{ \nu_f^{\idealm}(p^e)}{p^e} \]
the \emph{$F$-threshold of $I$ with respect to $J$}.  These numbers are also rational, when they are finite.
If $I = (f)$ is principal, then we call $\ft^{J}(f) := \ft^J(I)$  the \emph{$F$-threshold of $f$ with respect to $J$}, 
and $\ft^{\idealm}(I)$ is the \emph{$F$-pure threshold of $I$}. 
Like $F$-pure thresholds, the $F$-thresholds of $I$ can also be defined in terms of its test ideals.

@@

{\color{red} Make this consistent with the introduction.  The point is that we have already described how to get the {\tt nu}-s from their limit.  Maybe we should directly cite }.

@@

The option {\tt ContainmentTest} for the function {\tt nu} can be set to {\tt FrobeniusPower}, {\tt FrobeniusRoot}, or {\tt StandardPower}. The default value of this option depends on what is passed to {\tt nu}. Indeed, by default, {\tt ContainmentTest} is set to {\tt FrobeniusRoot} if the second argument passed to {\tt nu} is a polynomial, and is set to {\tt StandardPower} if it is an ideal.  We describe the consequences of setting {\tt ContainmentTest} to each of these values below, using an ideal $I$ as the second argument of $\nu$, since the option works analogously when $I$ is replaced with a polynomial $f$.

@@

Finally, suppose that {\tt ContainmentTest} is set to {\tt FrobeniusPower}.  Instead of producing the invariant $\nu_I^J(p^e)$, in this case the {\tt nu} function instead outputs the maximal integer $n$ such that the $n^{\textrm{th}}$ (generalized) Frobenius power of $I$ is not contained in the $p^e$-th Frobenius power of $J$ \cite{hernandez+etal.frobenius_powers}.  Note that this coincides with $\nu_I^J(p^e)$ when $I$ is replaced with a polynomial, or is a principal ideal.
After appropriately normalizing and taking the limit of these values as $e$ approaches infinity, these new values limit to certain \emph{critical exponents} (see \emph{loc.~cit.}).

Here, the $n^{\textrm{th}}$ Frobenius power of $I$, when $n$ is a nonnegative integer, is as defined in the paper {\it Frobenius Powers} by Hernández, Teixeira, and Witt.
In particular, {\tt nu(e,I,J)} and {\tt nu(e,I,J,ContainmentTest=>FrobeniusPower)} need not agree.  However, they will agree when $I$ is a principal ideal.

@@

The function {\tt nu} works by searching through the list of potential integers $n$ and checking containments of $I^n$ in a specified Frobenius power of $J$.  The way this search is approached is specified by the option {\tt Search}, which can be set to {\tt Binary} (the default value) or {\tt Linear}.

@@

The option {\tt ReturnList} (default value {\tt false}) can be used to request that the output be not only $\nu_I^J(p^e)$, but a list contaning $\nu_I^J(p^i)$, for $i=0,\ldots,e$.

%nu(5, f, ReturnList => true)

Alternatively, the option {\tt Verbose} (default value {\tt false}) can be used to request that the values $\nu_I^J(p^i)$ ($i=0,\ldots,e$) be printed as they are computed, to monitor the progress of the computation.

>>>>

We conclude this subsection by briefly reviewing some natural generalizations.  Suppose that $I$ and $J$ are ideals.  If $I$ is contained in the radical of $J$, then we set
%
\[ \nu_I^J(p^e) = \max \{ n : I^n \notin J^{[p^e]} \}. \]  
Otherwise, we set $\nu_I^J(p^e) = \infty$.  
This clearly generalizes the quantity $\nu_f^{\idealm}(p^e)$ considered earlier, and we call 
\[ \ft^J(I) := \lim_{e \to \infty} \frac{ \nu_f^{\idealm}(p^e)}{p^e} \]
the \emph{$F$-threshold of $I$ with respect to $J$}.  These numbers are also rational, when they are finite.
The value $\ft^{\idealm}(I)$ is called the \emph{$F$-pure threshold of $I$}, and if $I = (f)$ is principal,  $\ft^{J}(f) := \ft^J(I)$ is called the \emph{$F$-threshold of $f$ with respect to $J$}.
Like $F$-pure thresholds, $F$-thresholds can also be defined in terms of its test ideals.

@@

@@

The function {\tt nu} works by searching through the list of potential integers $n$ and checking containments of the $n^\text{the}$ power of $I$ in a specified Frobenius power of $J$.  
The user can specify how this search is approached through the  option {\tt Search}.  Namely, a binary search is used when {\tt Search} is set to {\tt Binary} (and this is the default value), and a linear search is run when it is set to {\tt Linear}.

The option {\tt ReturnList} for {\tt nu} (whose default value is {\tt false}) can be set to {\tt true} so that instead of outputting $\nu_I^J(p^e)$, but a list contaning $\nu_I^J(p^i)$, for $i=0,\ldots,e$.
Alternatively, the option {\tt Verbose} can be set to  to request that the values $\nu_I^J(p^i)$ ($i=0,\ldots,e$) be printed as they are computed, to monitor the progress of the computation.

Finally, we describe the option {\tt ContainmentTest} for the function {\tt nu}.
This option can be set to {\tt FrobeniusPower}, {\tt FrobeniusRoot}, or {\tt StandardPower}. The default value of this option depends on what is passed to {\tt nu}. Indeed, by default, {\tt ContainmentTest} is set to {\tt FrobeniusRoot} if the second argument passed to {\tt nu} is a polynomial, and is set to {\tt StandardPower} if it is an ideal.  We describe the consequences of setting {\tt ContainmentTest} to each of these values below, using an ideal $I$ as the second argument of $\nu$, since the option works analogously when $I$ is replaced with a polynomial $f$.

@@

Finally, suppose that {\tt ContainmentTest} is set to {\tt FrobeniusPower}.  Instead of producing the invariant $\nu_I^J(p^e)$, in this case the {\tt nu} function instead outputs the maximal integer $n$ such that the $n^{\textrm{th}}$ \emph{(generalized) Frobenius power} of $I$ is not contained in the $p^e$-th Frobenius power of $J$ \cite{hernandez+etal.frobenius_powers}. 
Note that the resulting value coincides with $\nu_I^J(p^e)$ when $I$ is replaced with a polynomial, or is a principal ideal, but need not coincide in general.
In line with the philosophy described in the introduction, after appropriately normalizing and taking the limit of these values as $e$ approaches infinity, these new values limit to certain invariants of interest called \emph{critical exponents} (see \emph{loc.~cit.}).

@@

@@
